---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE
)
```

## CanadaC19

The  CanadaC19 package harvests the data made freely available by the this [repository](https://github.com/ishaberry/Covid19Canada). This package is currently a component to the [Covid19R project](https://github.com/Covid19R). 

## Installation (once on CRAN)

``` {r install, eval=FALSE}
install.packages("CanadaC19")
```

Get the latest development version from [github](https://github.com/debusklaneml/CanadaC19)

```{r install_github, eval = FALSE}
devtools::install_github("debusklaneml/CanadaC19")
```


## Getting the Most Up to Date Data

To get the most updated data, run the following functions

```{r refresh, eval=FALSE}
new_data <- refresh_CanadaC19_cases()
```

## Columns

The data follows the [covid19R standard for tidy Covid-19 data](https://covid19r.github.io/documentation/data-format-standard.html). 



