---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE
)
```

## CanadaC19

### Tests

### Files to edit and things to do for release to the public
- Readme.Rmd: We have provided a skeleton of your readme within this file. Use it and fill it in as needed. Feel free to modify as you'd like.

- News.md: Sub in your R project name for the first release

- Make a [pkgdown](https://pkgdown.r-lib.org/) site! This can be as simple as running `pkgdown::build_site()`, pushing the update, and making sure your repo settings are set to put up the website. Add the URL to your README and your github repo

### Making your package a part of the Covid19R Project

OK! You're there! It works, and your build is more or less clean (at least, only notes). Close your issue about developing a new package and... [file a new issue to onboard this package](https://github.com/Covid19R/covid19R/issues) with the onboarding template! We'll take a look, test it out, and if it's ready, we'll add it in! Nice work! (and if it's not, we'll help you fix it)

### Submitting to CRAN
- Use RStudio to build check your package until there are no errors, warnings, or notes, even! Run the suite of devtools checks provided in setupcode.R. If you pass everything, use devtools to submit (it's in the setupcode), as it will ask you additional questions.

- Make sure your cran-comments.md file is up to date with info from your final check!

-----------

# YOUR_PACKAGE_NAME

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-orange.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![CRAN status](https://www.r-pkg.org/badges/version/YOUR_PACKAGE)](https://CRAN.R-project.org/package=YOUR_PACKAGE)
[![Travis build status](https://travis-ci.org/Covid19R/YOUR_PACKAGE.svg?branch=master)](https://travis-ci.org/USER_OR_ORG/YOUR_PACKAGE)
<!-- badges: end -->

The  YOUR_PACKAGE package harvests the data made freely available by the XXX. See USEFUL_URL_ABOUT_DATA for more.

## Installation

ONLY INCLUDE IF SUBMITTED TO/ON CRAN You can install the released version of covid19nytimes from [CRAN](https://CRAN.R-project.org) with:

``` {r install, eval=FALSE}
install.packages("YOUR_PACKAGE")
```

Or the latest development version from [github](https://github.com/USER_OR_ORG/YOUR_PACKAGE)

```{r install_github, eval = FALSE}
devtools::install_github("USER_OR_ORG/YOUR_PACKAGE")
```

## Data

The package has the data from XXXXXX. The package comes with static data that was downloaded at the time of the last package update.

```{r head_of_data, eval = FALSE}
library(YOUR_LIBRARY_NAME)

head(DATA) %>% knitr::kable()

```

## Getting the Most Up to Date Data

To get the most updated data, run the following functions

```{r refresh}
```

## Columns

The data follows the [covid19R standard for tidy Covid-19 data](https://covid19r.github.io/documentation/data-format-standard.html). The data columns are as follows:

* date - The date in YYYY-MM-DD form
* location - The name of the location as provided by the data source. Nested locations are combined and separated by a `,`, and can be split by `tidyr::separate()`, if you wish.
* location_type - The type of location using the [Covid19R Controlled Vocabulary](https://covid19r.github.io/documentation/standardized-vocabulary.html). Nested locations are indicated by multiple location types being combined with a `_`
* location_code - A standardized location code using a national or international standard. MORE HERE
* location_code_type The type of standardized location code being used according to the covid19R controlled vocabulary. Here we use `XXX`
* data_type - the type of data in that given row from the [Covid19R Controlled Vocabulary](https://covid19r.github.io/documentation/standardized-vocabulary.html). What is here?
* value - number of cases of each data type
* OTHER COLUMNS - WHAT THEY MEAN

## Sample visualization

```{r example_plot}
```
